R Notebook

### 2023-06-13 draft_work.Rmd
Began Work Adding Leaflet Map For USA Visitors per Region

```{r}
library(broom)
library(factoextra)
```

>>>>

```{r}
library(broom)
library(factoextra)
library(sf)
```

```{r}
usa_visit_spend_region %>%
  group_by(region) %>% 
  summarise(mean_spend = mean(spend),
            mean_visits = mean(visits)) %>% 
  ggplot(aes(x = mean_visits, y = mean_spend, colour = region)) +
  geom_point()
```

```{r}
usa_visit_spend_region %>% 
  ggplot(aes(x = year, y = visits, colour = region, group = region)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019))
```

```{r}
usa_visit_spend_region %>% 
  ggplot(aes(x = year, y = spend, colour = region, group = region)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019))
```

```{r}
library(leaflet)
library(leafpop)
```

```{r}

pal <- colorNumeric(
  palette = "Reds",
  domain = usa_visit_spend_region$visits)

usa_visit_spend_region %>%
  filter(year == 2019) %>% 
  leaflet() %>%
  addTiles() %>% 
  addCircleMarkers(lng = ~long.x,
                   lat = ~lat.x,
                   color = ~pal(visits)) %>% 
                   # popup = ~paste(location, "<br> Spend:", spend, "<br> Visits:", visits)) %>% 
  addLegend(position = "bottomright", pal = geo_palette, values = ~visits, opacity = 2, title = "Visits") %>% 
  addControl(position = "topright", html = title)
```

----------------------------------------------------------------

----------------------------------------------------------------

```{r}
scotland_regions <- st_read(dsn = "geo/", # Data Source Name/Path
                          layer = "SG_ScottishPoliceDivisions_2019")
```

```{r}
glimpse(scotland_regions)
```

```{r}
scotland_regions$PDivName
```

```{r}
ggplot(scotland_regions) +
  geom_sf(fill = "antiquewhite")
```
